\section{Patent}

\subsection{Introduction}

\subsubsection{Basic Patent Procedure}

\begin{enumerate}
    \item File for a patent with the PTO.
    \item An examiner is assigned to the application. The review process takes 
    two to four years on average.
    \item Applicants can appeal adverse rulings of the PTO Board of Appeals to a 
    federal appellate court.
    \begin{enumerate}
        \item Pre-1982: Court of Customs and Patent Appeals.
        \item 1982 and on: U.S. Court of Appeals for the Federal Circuit.
    \end{enumerate}
\end{enumerate}

\subsubsection{History}

\begin{enumerate}
    \item First patent system: Venice, fifteenth century.\footnote{Casebook p. 
    123.}
    \item 
    \item First U.S. patent statute: 1790.
    \item 1952: Patent Act.
    \item 1982: Federal Courts Improvement Act. Created the Federal Circuit. 
    Aimed to unify patent doctrine, and had the effect of strengthening patent 
    protections.\footnote{Casebook p. 127.}
\end{enumerate}

\subsubsection{Overview of the Patent Laws}

\paragraph{Requirements for Patentability}

\begin{enumerate}
    \item \textbf{Subject matter}.\footnote{Casebook pp. 128--29.}
    \item \textbf{Novelty}: not preceded in identical form by prior public art. 
    35 U.S.C. \S\ 102.
    \item \textbf{Utility}: it must be useful (a low barrier). 35 U.S.C. \S\ 
    101.
    \item \textbf{Nonobviousness}: a nontrivial extension of what was known (the 
    most important requirement). 35 U.S.C. \S\ 103.
    \item \textbf{Disclosure and enablement}: disclosed in a way that enables a 
    person having ordinary skill in the art (PHOSITA) to make and use the 
    invention. 35 U.S.C. \S\ 112.
\end{enumerate}

\paragraph{Rights Conferred by a Patent}

\begin{enumerate}
    \item \textbf{Claims}: boundaries of the property right the patent 
    confers.\footnote{Casebook p. 129.}
    \item \textbf{Specification}: describes the invention.
    \item Patents confer exclusive rights for a term of years.\footnote{Casebook 
    p. 130.}
    \begin{enumerate}
        \item Post--GATT-TRIPS (1995): 20 years from the filing date.
        \item Previously: 17 years from the date the USPTO issued the patent.
    \end{enumerate}
    \item Patent rights are negative, i.e., they let you prevent others from 
    acting.
\end{enumerate}

\subsubsection{Theories of Patent Law}

\begin{enumerate}
    \item Patents give a market-driven incentive to invest in 
    innovation.\footnote{Casebook p. 131.}
\end{enumerate}

\subsection{Elements of Patentability}

\subsubsection{Patentable Subject Matter}

\paragraph{35 U.S.C. \S\ 101: Inventions Patentable}

\begin{enumerate}
    \item ``Whoever invents or discovers any new and useful process, machine, 
    manufacture, or composition of matter, or any new and useful improvement 
    thereof, may obtain a patent therefor, subject to the conditions and 
    requirements of this title.''
\end{enumerate}

\paragraph{Compositions of Matter: \emph{Diamond v. Chakrabarty}}

\begin{enumerate}
    \item Chakrabarty invented a genetically engineered version of pseudomonas 
    to break down hydrocarbons to help with oil spill cleanups.
    \item Three claims:\footnote{Casebook p. 129.}
    \begin{enumerate}
        \item The \textbf{process} of creating the bacteria.
        \item An ``inoculum,'' including a carrier (a \textbf{combination} 
        claim).
        \item ``~.~.~.~the bacteria themselves.''
    \end{enumerate}
    \item Patentable subject matter comprises ``anything under the sun that is 
    made by [humans].''
    \item Things that are \emph{not} patentable:
    \begin{enumerate}
        \item Laws of nature---e.g., Newton's law of gravitation.
        \item Physical phenomena---e.g., naturally occurring plants or minerals.
        \item Abstract ideas---e.g., E=mc\textsuperscript{2}.
    \end{enumerate}
    \item Chakrabarty's bacterium was not naturally occurring. Rather, it was 
    \textbf{``a product of human ingenuity~.~.~.~.''}---``not nature's 
    handiwork, but his own.''
\end{enumerate}

\paragraph{Abstract Ideas: \emph{Bilski v. Kappos}} 
~\\\\
Rather than adopt categorical rules, the Supreme Court held narrowly that the 
hedging technique in question was not patentable because it was an abstract 
idea.

The Federal Circuit's machine-or-transformation test is \emph{not} the sole 
test for what counts as a ``process.'' Business methods \emph{are} protectable 
today.\footnote{Merges, \emph{Six Impossible Patents before Breakfast}, 
\url{http://scholarship.law.berkeley.edu/cgi/viewcontent.cgi?article=1162&context=facpubs}.}

Unpatentable abstractions include things like risk hedging or algorithms. But 
the specific applications of these abstract ideas may be patentable.

\begin{enumerate}
    \item Bilski patented a commodity price hedging technique known as the fixed 
    price contract. He called it a ``method.'' He also made a dependent claim, 
    which applied the general method to energy markets.
    \item Held: this process did not physically transform anything (compared to, 
    e.g., a chemical process).
    \item Federal circuit (which the Supreme Court rejected):
    \begin{enumerate}
        \item 
        \item \textbf{Machine or transformation test}: to be patentable, a 
        process must either:
        \begin{enumerate}
            \item Transform an article to a different state or thing, and/or
            \item Be ``tied to a particular machine.''
        \end{enumerate}
    \end{enumerate}
    \item Supreme Court:
    \begin{enumerate}
        \item Four categories of patentable subject matter:
        \begin{enumerate}
            \item Process.
            \item Machine. 
            \item Manufacture.
            \item Composition of matter.
        \end{enumerate}
        \item Three exceptions (derived from the requirement that patentable 
        inventions be new and useful):
        \begin{enumerate}
            \item Laws of nature.
            \item Physical phenomena.
            \item Abstract ideas.
        \end{enumerate}
    \end{enumerate}
    \item Justice Kennedy, concurring: the machine-or-transformation test might 
    be useful for Industrial Age inventions, but it may not be well suited to 
    the Information Age.
    \item Justice Stevens, dissenting: business methods are categorically 
    unpatentable as processes under \S\ 101.
\end{enumerate}

\paragraph{Preemption: \emph{Mayo v. Prometheus}}

\begin{enumerate}
    \item ``The Court has repeatedly emphasized~.~.~.~a concern that patent 
    law not inhibit further discovery by \textbf{improperly tying up} the 
    future use of laws of nature.
    \item Preemption = overbreadth.
    \item Purpose of \S\ 101: preserve the ``basic tools'' of scientific 
    discovery for common use.
\end{enumerate}

\paragraph{Genes: \emph{AMP v. Myriad Genetics, Inc.}}

\begin{enumerate}
    \item \emph{Myriad} decided only the subject matter threshold.
    \item Are human DNA sequences patentable?
    \item Is isolating DNA a inventive act that gives patent rights to the one 
    who isolated it?
    \item Supreme Court:
    \begin{enumerate}
        \item Naturally occurring DNA segments are not patentable, even if the 
        isolation involved significant effort. Cf. \emph{Chakrabarty}.
        \item But non--naturally occurring cDNA is patentable because it's the 
        product of human invention.
    \end{enumerate}
\end{enumerate}

\subsubsection{Utility}

\begin{enumerate}
    \item \S\ 101: ``Whoever invents or discovers any new \textbf{and useful} 
    process~.~.~.~''
    \item No patents for:
    \begin{enumerate}
        \item \textbf{No known utility}, e.g., perpetual motion machines.
        \item \textbf{Malicious utility} (Justice Story).
    \end{enumerate}
    \item What about new chemical compounds with no known uses?
    \item The presumption is that an invention is useful. The PTO bears the 
    burden of disproving utility.
\end{enumerate}

\paragraph{Promising \emph{Experimental} Results---Not Patentable: 
\emph{Brenner v.  Manson}}

\begin{enumerate}
    \item Patents cannot be granted for chemical compounds with no known uses. 
    ``~.~.~.~a patent is not a hunting license. It is not a reward for the 
    search, but compensation for its successful 
    conclusion.''\footnote{Casebook p. 179.}
\end{enumerate}

\paragraph{Promising \emph{Clinical} Results---Patentable: \emph{In re Brana}}

\begin{enumerate}
    \item Results from mice testing suggest efficacy in humans, so they pass 
    the utility threshold.\footnote{Casebook p. 181.}
\end{enumerate}

\paragraph{Timing: \emph{In re Fisher}}

\begin{enumerate}
    \item The underlying genes in question had no known function.
    \item Held: utility was too attenuated. The patent would have been a 
    hunting license.
    \item Applicant must show utility as of the filing date.\footnote{Casebook 
    p. 182--85.}
\end{enumerate}

\paragraph{Patent Office Utility Guidelines}

\begin{enumerate}
    \item It has to actually work.\footnote{Casebook p. 185--87.}
\end{enumerate}

\paragraph{Moral Utility}

\begin{enumerate}
    \item Historically, often used to deny gambling patents.\footnote{Casebook 
    p. 187--88.}
\end{enumerate}

\paragraph{Designed to Deceive: \emph{Juicy Whip, Inc. v. Orange Bang, Inc.}} 

\begin{enumerate}
    \item Deceptive inventions are patentable.
    \item ``All that the law requires is, that the invention should not be 
    frivolous or injurious to the well-being, good policy, or sound morals of 
    society. The word "useful," therefore, is incorporated into the act in 
    contradistinction to mischievous or immoral.'' \emph{Lowell v. Lewis}, 15 
    F. Cas. 1018, 1019 (CC Mass. 1817).
    \item Deception can be useful---e.g., cubic zirconium.
\end{enumerate}

\subsubsection{Written Description and Enablement}

\paragraph{35 U.S.C. \S\ 112}

\begin{enumerate}
    \item Must contain a \textbf{written description} that can 
    \textbf{``enable any person skilled in the art''} to make it.
\end{enumerate}

\paragraph{Overly Broad Claims and Enablement: \emph{The Incandescent Lamp 
Patent}}

\begin{enumerate}
    \item Sawyer and Man had a patent on a lightbulb involving ``fibrous or 
    textile material.'' They tried to assert it against Edison, who was using 
    bamboo in his own bulbs.\footnote{Casebook p. 196 ff.}
    \item S\&M tried to monopolize the use of ``all fibrous or textile 
    material'' in lightbulbs. But they had only tried a few types. They hadn't 
    discovered ``a quality common to them all,'' so their claim was too broad.  
    Their claim would have included over 6,000 types of plants and products, 
    but really they had only tested a few.
    \item The S\&M patent only enabled the use of the materials they had 
    tested (carbonized paper, etc.).
\end{enumerate}

\paragraph{Written Description: \emph{The Gentry Gallery, Inc. v. 
The Berkline Corp.}}

\begin{enumerate}
    \item Claims are limited to the written description.
    \item ``~.~.~.~the scope of the right to exclude may be limited by a 
    narrow disclosure.''\footnote{Casebook p. 208.} Gentry's patent only 
    described the placement of recliner controls inside the console, so it 
    could not prevent its competitors from placing controls elsewhere.
\end{enumerate}

\paragraph{\emph{Ariad Pharmaceuticals, Inc. v. Eli Lilly \& Co.}}

\begin{enumerate}
    \item The written description requirement requires the disclosure of 
    actual structures and actual working examples in order to justify the 
    broad scope of a claim.
    \item \S\ 112 excludes inventions from patent protection due to inadequate 
    disclosure. Compare to \S\ 101, which excludes entire \emph{categories} 
    for overbreadth.
\end{enumerate}

\subsubsection{Novelty and Statutory Bars}

\paragraph{Novelty}

\begin{enumerate}
    \item Old law (1952 Act): \textbf{first to invent}. Defines novelty from 
    the \emph{date of first invention}.
    \item New law (AIA, 2011): \textbf{first to file}. Novelty is measured as 
    of the \emph{date of the patent application}. Takes effect for patents 
    filed on or after March 16, 2013.\footnote{Casebook p. 226.}
    \item \textbf{Novelty}: \emph{newness}. Was it new compared to the prior 
    art? 35 U.S.C. \S\ 102(a).
    \item \textbf{Statutory bar}: \emph{timeliness}. A bar based on too long a 
    delay in seeking patent protection. Did the inventor file soon enough? \S\ 
    102(b).
\end{enumerate}

\paragraph{Main Issues under Novelty}

\begin{enumerate}
    \item \textbf{Reference}: a single piece of prior art.
    \item \textbf{Timing}: what does the prior art include?
    \item \textbf{Similarity}: how similar must prior art be to anticipate 
    (i.e., destroy) a patent?
    \item \textbf{Categories of prior art}---35 U.S.C. \S\ 102(a)(1):
    \begin{enumerate}
        \item Patented.
        \item Described in a printed publication.
        \item In public use, on sale, or otherwise available to the public.
    \end{enumerate}
\end{enumerate}

\paragraph{Statutory Bars}

\begin{enumerate}
    \item Under \S\ 102(b), an inventor loses the right to patent if, more 
    than one year prior to filing, the invention was:
    \begin{enumerate}
        \item Patented by another elsewhere.
        \item Patented by the applicant in a foreign country.
        \item Described in a printed publication anywhere.
        \item In public use in the United States.
        \item On sale in the U.S.
    \end{enumerate}
\end{enumerate}

\paragraph{35 U.S.C. \S\ 102 (1952): Conditions for patentability; novelty and 
loss of right to patent}

\begin{enumerate}
    \item (a) Novelty.
    \item (b) Statutory Bars.
    \item (c), (d): (omitted).
    \item (e) Secret Prior Art: Previously filed applications.
    \item (f) Derivation.
    \item (g) (inteference proceedings).
\end{enumerate}

\paragraph{Novelty: \emph{Rosaire v. National Lead Co.}}
~\\\\
Issue: \S\ 102(a) bars patentability if the invention was ``known or used by 
others.'' What does it mean to be known or used?

Held: earlier use, even if not published, establishes prior art. I.e., 
``public'' means ``not explicitly private.'' This is a very liberal definition 
of prior art. See \emph{Hall} below.

\begin{enumerate}
    \item 1936: Rosaire and Horovitz patented a method for analyzing soil to 
    detect nearby oil.\footnote{Casebook p. 228.}
    \item National Lead argued that the patent was invalid and that there had 
    been no infringement.
    \item Rosaire admitted that Teplitz first invented the method, but argued 
    that Teplitz did not publish his ideas and that they were experimental.
    \item Held: Teplitz use was actual, not experimental, and that publication 
    was not required as long as Teplitz did the work openly.
\end{enumerate}

\paragraph{\emph{Inherency Doctrine}} 

\begin{enumerate}
    \item If somebody accidentally comes up with an invention, is that 
    invention prior art if somebody later deliberately invents the same thing? 
    Courts are divided. Newer cases have focused on whether the earlier 
    invention provided a public benefit.\footnote{Casebook p. 233.}
\end{enumerate}

\paragraph{Statutory Bars---Defining ``Publication'': \emph{In Re Hall}}
~\\\\
Publication of a single copy in a foreign university library can satisfy 
the publication limitation.

\begin{itemize}
    \item Hall applied for a chemical patent. The PTO rejected it because the 
    same process had been published in a German doctoral dissertation more than 
    a year earlier.\footnote{Casebook p. 234.}
    \item On appeal, the court held that publication in a university library was 
    ``sufficiently accessible, at least to the public interested in the art, so 
    that such a one by examining the reference could make the claimed invention 
    without further research or experimentation.''\footnote{Casebook p. 235.} 
    Affirmed.
\end{itemize}

\paragraph{Statutory Bars---Public Use: \emph{Egbert v. Lippmann}}
~\\\\
Hidden use (i.e., ``non-informing public use'') can still be public use. The 
inventor here slept on his rights for 11 years.

\begin{enumerate}
    \item Barnes invented a new type of corset spring in 1855 but did not apply 
    for a patent until 1866. In the meantime, he had given at least two pairs to 
    Frances, who later became his wife and the assignee of the 
    patent.\footnote{Casebook pp. 237--39.}
    \item Frances sued for patent infringement. The question was whether the 
    invention had been in public use for more than two years\footnote{Now the 
    period is one year.} before the patent application.
    \item The Court (Justice Woods) held that it was a public use because (1) a 
    single use is enough, (2) giving the invention to one person is enough, and 
    (3) selling a hidden component of a public machine is still public use.
    \item Justice Miller, dissenting: if a hidden corset spring is a public use, 
    how can anything be a private use?\footnote{Casebook p. 240.}
\end{enumerate}

\paragraph{Experimental Use Exception: \emph{City of Elizabeth v. Pavement 
Company}}
~\\\\
Experimental use is not public use.

\begin{enumerate}
    \item Nicholson was issued a patent for wooden pavement in 1854. He had been 
    testing the design for the previous six years on a public street in 
    Boston.\footnote{Casebook pp. 243--44.}
    \item Nicholson sued the City of Elizabeth for infringement. Elizabeth 
    argued that the patent was invalid because the invention was in public use.
    \item The court held that experimental use is an exception to the public use 
    restriction. Here, Nicholson intended the use to be experimental, and the 
    public's use was only ``incidental.''\footnote{Casebook pp. 245--46.}
\end{enumerate}

\paragraph{Priority under the 1952 Act: 35 U.S.C. \S\ 102: Novelty and Loss of 
Right}

\begin{enumerate}
    \item Priority is about being \textbf{first}. Novelty is about being 
    \textbf{new}.
    \item A person gets a patent unless:
    \begin{enumerate}
        \item (g)(1) during the course of an interference, another inventor (from 
        any WTO country) establishes that he got there first, or
        \item (g)(2) another U.S. inventor made the invention first.
    \end{enumerate}
    \item ``~.~.~.~priority generally goes to the first inventor to (1) reduce 
    an invention to practice, without (2) abandoning the 
    invention.''\footnote{Casebook p. 248.} An exception arises if the inventor 
    was not the first to reduce to practice but was reasonably diligent in doing 
    so.
    \item AIA sweeps away this complexity in favor of a first-to-file 
    system---see below. 
\end{enumerate}

\paragraph{Priority and the Reasonable Diligence Exception: \emph{Griffith v. 
Kanamaru}}
~\\\\
Delays to make an invention more marketable do not fall within the reasonable 
diligence exception. In other words, you don't get priority if you 
unreasonably delayed reduction to practice.

\begin{enumerate}
    \item Griffith and Kanamaru both invented the same compound.
    \item Timeline:
    \begin{enumerate}
        \item June 30, 1981: Griffith established conception.
        \item November 17, 1982: Kanamaru filed for a patent.
        \item June 15, 1983 to September 13. 1983: Griffith was inactive.
        \item January 11, 1984: Griffith reduced to practice.
    \end{enumerate}
    \item Griffith argued that he was reasonably diligent in reducing the 
    invention to practice while (1) he sought funding, as a form of peer review, 
    and (2) awaited the matriculation of a particular grad student, even though 
    there were other students who could have done the work.\footnote{Casebook p. 
    250.}
    \item The court held that the reasonable diligence exception applies to 
    ``everyday problems and limitations'' (e.g., illness), but held that delays 
    in order to ``refine an invention to the most marketable and profitable form 
    have not been accepted as sufficient excuses for 
    inactivity.''\footnote{Casebook p. 250--51.}
    \item Held (affirming the PTO): Griffith failed to establish a prime facie 
    case of reasonable diligence or a sufficient excuse for 
    inactivity.\footnote{Casebook p. 251.}
\end{enumerate}

\paragraph{Prior User Rights}

\begin{enumerate}
    \item Under the 1952 act, a patent holder can exclude another who 
    independently developed the same invention from using it.
    \item The AIA addressed this problem by granting ``prior user rights'' to 
    non-patentees who were using the invention before someone else patented it, 
    with some limitations (e.g., non-transferability).\footnote{Casebook p. 252.}
\end{enumerate}

\paragraph{Novelty, Priority, and Statutory Bars under the AIA}

\begin{enumerate}
    \item The AIA introduced \textbf{three main changes regarding novelty and 
    priority}:\footnote{Casebook p. 253.}
    \begin{enumerate}
        \item The critical date is when a patent is first filed.
        \item Relevant prior art consists of all references available prior to 
        the filing date, with a one-year grace period.
        \item Priority contests will be determined by filing dates.
    \end{enumerate}
    \item \textbf{Structure}:
    \begin{enumerate}
        \item 102(a) Novelty; Prior Art: patent granted unless---
        \begin{enumerate}
            \item (1) Published before filing date.
            \item (2) Described in another previously filed patent.
            \item 
        \end{enumerate}
        \item (b) Exceptions---
        \begin{enumerate}
            \item (1) Disclosure made less than one year before filing is not 
            prior art if---
            \begin{enumerate}
                \item Made by the inventor.
                \item Based on information from the inventor.
            \end{enumerate}
            \item (2) Disclosure is not prior art under (a)(2) if---
            \begin{enumerate}
                \item Subject matter was obtained from the inventor.
                \item Subject matter had been disclosed by the inventor.
                \item Subject matter disclosed and invention were owned by the 
                same person.
            \end{enumerate}
        \end{enumerate}
    \end{enumerate}
    \item No \textbf{geographic restrictions} on prior 
    art.\footnote{Casebook p. 254.}
    \item \textbf{Novelty vs. priority}:
    \begin{enumerate}
        \item Priority: inventor vs. inventor. Who invented it first?
        \item Novelty: inventor vs. prior art. Is it new?
        \item The AIA only asks \textbf{who filed first} (including the one 
        year grace period).\footnote{Casebook pp. 244--45.}
    \end{enumerate}
\end{enumerate}

\paragraph{Grace period under the AIA}

\begin{enumerate}
    \item Generally, under the AIA, an application has to be filed before a 
    prior art event.
    \item But there's a grace period exception. A disclosure (i.e., any prior 
    art reference) is eligible for the grace period if made by the inventor or 
    if the inventor himself previously made a public 
    disclosure.\footnote{Casebook p. 255.}
    \begin{enumerate}
        \item Under the 1952 act, independent third-party disclosure 
        \emph{\textbf{did}} create a grace period. Not so under the 
        AIA.\footnote{Casebook p. 256.}
        \item ``In public use'' or ``on sale'' (AIA \S\ 102) can refer to 
        confidential activity. For instance, an inventor's \textbf{non-informing 
        public use} is a disclosure (but not third-party non-informing 
        uses).\footnote{Casebook p. 257.}
    \end{enumerate}
\end{enumerate}

\subsubsection{Nonobviousness}

\paragraph{35 U.S.C. \S\ 103}
~\\\\
\begin{enumerate}
    \item ``A patent for a claimed invention may not be obtained, 
    notwithstanding that the claimed invention is not identically disclosed as 
    set forth in section 102, if the \emph{differences} between the claimed 
    invention and the prior art are such that the claimed invention as a whole 
    \textbf{would have been obvious} before the effective filing date of the 
    claimed invention \textbf{to a person having ordinary skill in the art} to 
    which the claimed invention pertains. Patentability shall not be negated 
    by the manner in which the invention was made.''
    \item Policy: avoid a profusion of paltry patents.
    \item Another policy: obvious patents may compromise the incentives to 
    make nonobvious inventions.
    \item Merges: ``the primary gatekeeper of the patent system.''
\end{enumerate}

\paragraph{Testing for Obviousness: \emph{Graham v. John Deere Co.}}
~\\\\
\S\ 103 requires an ``inventive leap.''\footnote{Casebook p. 269.} Minor obvious 
improvements don't qualify.

\begin{enumerate}
    \item First case interpreting \S\ 103.
    \item History of the patent system: Jefferson; \enquote{limited monopoly 
    might serve to incite \enquote{ingenuity}~.~.~.~.}\footnote{Casebook p. 
    259--61.}
    \item First appearance of nonobviousness: \emph{Hotchkiss v. Greenwood}, 
    1851. Codified in \S\ 103.\footnote{Casebook p. 261--62.}
    \item \emph{Graham}'s \S\ 103 test:\footnote{Casebook pp. 262--63.}
    \begin{enumerate}
        \item Determine scope and content of the prior art.
        \item Determine differences between prior art and the claims.
        \item Determine the level of ordinary skill in the art.
        \item Evaluate obviousness.
        \item Secondary considerations: commercial success, long felt need, 
        failure of others.
    \end{enumerate}
    \item 1950: Graham got a patent on a shock absorber for tractors ('811).
    \item 1953: Graham modified the design and got a second patent ('798), at 
    issue here. The main question was whether this improvement was obvious 
    (and therefore invalid).
    \item Graham argued that John Deere infringed the '798 patent.
    \item Another patent, held by Glencoe, had all the elements of the '798 
    patent.
    \item The Court found that the improvement in the '798 patent was obvious 
    and therefore invalid. It also found that the Glencoe patent was 
    mechanically identical.\footnote{Casebook p. 268.}
    \item The invention here was ``destitute of ingenuity''---``the work of 
    the skillful mechanic, not that of the inventor.''
\end{enumerate}

\paragraph{Rejecting the TSM Test in Favor of a Flexible Standard: \emph{KSR 
International Co. v. Teleflex Inc.}}
~\\\\
The Federal Circuit's ``teaching, suggestion, or motivation'' (TSM) test is 
too restrictive. The standard for nonobviousness is flexible.

\begin{enumerate}
    \item Engelgau patented a pedal assembly. Teleflex held the exclusive 
    license.\footnote{Casebook p. 269.}
    \item Teleflex sued KSR for infringement. KSR countered that the relevant 
    claim was invalid because its subject matter was obvious.
    \item The Federal Circuit had developed the ``teaching, suggestion, or 
    motivation'' \textbf{(TSM) test}, which holds a patent to be nonobvious 
    only if ``some motivation or suggestion to combine the prior art 
    teachings'' could be found in prior art, the nature of the problem, or the 
    knowledge of a person having ordinary skill in the art.\footnote{Casebook 
    p. 270.} In other words, the prior art has to explicitly say that the 
    combination shall happen.
    \item The PTO rejected one of Engelbau's other claims on the basis of 
    nonobviousness. It cited two other patents: an adjustable pedal (Redding) 
    and a method for mounting an electronic sensor on a pedal's support 
    structure (Smith). The PTO rejected the claim that simply put the two 
    together, but it allowed a variation on Redding using a fixed pivot 
    point.\footnote{Casebook p. 272--73.}
    \item The District Court found that the claim was obvious. It granted 
    summary judgment in favor of KSR. The Federal Circuit reversed because the 
    District Court had improperly applied its TSM test.\footnote{Casebook p. 
    273.}
    \item The Supreme Court here found that the TSM test was too formalistic 
    and restrictive. It argued for a broader, more flexible test---one that 
    allows for common sense. It found that Engelbau patent was obvious because 
    any person with ordinary skill in the art would have thought to combine 
    the other patents.  Reversed.\footnote{Casebook pp. 274--77.}
    \begin{enumerate}
        \item The TSM test excluded common sense, which made it hard for PTO 
        examiners to reject patents for obviousness, which led to a 
        proliferation of trivial patents.
        \item \textbf{New test}: ``If a person of ordinary skill can implement 
        a predictable variation, \S\ 103 likely bars its patentability.''
        \item District courts can grant summary judgment for obviousness.
    \end{enumerate}
\end{enumerate}

\paragraph{Nonobviousness and the AIA}

\begin{enumerate}
    \item Shifts the time for determining obviousness from the invention date 
    to the filing date.\footnote{Casebook p. 289.}
\end{enumerate}

\subsection{Administrative Procedures at the PTO}

\subsubsection{The AIA's New Administrative Procedures}

\begin{enumerate}
    \item The AIA created five new administrative 
    procedures:\footnote{Casebook p. 290.}
    \begin{enumerate}
        \item Post-grant review (PGR).
        \item Inter partes review (IPR).
        \item Supplemental examination.
        \item Transitional post-grant review for business method patents 
        (``covered business method'' review).
        \item Derivation proceedings.
    \end{enumerate}
    \item These are all about challenges to validity.
    \item Previously, there was no chance for third parties to challenge 
    validity until they were sued for infringement.
    \item Old procedures:
    \begin{enumerate}
        \item Reissue (still in existence). Only the patentee can request it. 
        Can be used to get a new patent when the original is invalid or 
        inoperative.
        \item Ex parte reexamination (also still in existence).
        \item Inter partes reexamination (replaced by inter partes review).
    \end{enumerate}
    \item Post-AIA: no concurrent proceedings allowed.
\end{enumerate}

\subsubsection{Post-Grant Review (PGR)}

\begin{enumerate}
    \item Anyone can challenge the validity of a patent within nine months of 
    issuance.\footnote{Casebook p. 290.}
    \item In effect, a mini-trial, as an alternative to district court 
    proceedings.
    \item In responding to a PGR complaint, the patent holder cannot introduce 
    new evidence of patentability.
    \item Appeals go to the Federal Circuit.\footnote{Casebook p. 292.}
    \item Can't file both a district court claim and a PGR 
    claim.\footnote{Casebook p. 293.}
    \item Issue preclusion from PGR applies to later district court 
    claims.
\end{enumerate}

\subsubsection{Inter Partes Review (IPR)}

\begin{enumerate}
    \item Anyone can request a review of an issued patent. The one requesting 
    review has to show that he'll likely prevail on at least one 
    claim.\footnote{Casebook p. 293.}
    \item Only patents and printed publications can be cited (because IPRs are 
    meant to be efficient and streamlined).\footnote{Casebook p. 293--94.}
    \item Estoppel applies.
    \item Can only follow a PGR decision or the nine-month PGR window.
    \item Can only review \S\S\ 102 (novelty) and 103 (obviousness).
\end{enumerate}

\subsubsection{Derivation Proceeding}

\begin{enumerate}
    \item Responds to the fear that some might try to steal an invention and 
    file it first.\footnote{Casebook p. 295.}
    \item This is a ``special administrative proceeding to sort out claims that 
    one applicant stole or `derived' an invention of another.''
    \item Must be brought within one year of patent publication (or unpublished 
    patent issuance).
\end{enumerate}

\subsection{Infringement}

\begin{enumerate}
    \item Definition of ``infringement'': the accused product has \emph{every 
    element} of the claim.
\end{enumerate}

\subsubsection{Claim Interpretation}

\begin{enumerate}
    \item Claims define the boundaries of the owner's property 
    right.\footnote{Casebook p. 295.}
    \item To a businessman, the claim is the shelf space, the bottom line.
    \item \textbf{Broader claims are more valuable but easier to invalidate on 
    the basis of prior art.} ``[T]he stronger a patent the weaker it is and the 
    weaker a patent the stronger it is.''\footnote{Casebook p. 296.}
    \item ``Literal infringement'': the infringing product is within the scope 
    of the claims.
\end{enumerate}

\paragraph{Canons of Claim Construction}

\begin{enumerate}
    \item \textbf{Claim differentiation} (use of a term in one claim can 
    suggest its meaning when used in another claim).
    \item \textbf{Interpretation in light of purpose}.
    \item \textbf{Plain meaning vs. contextual meaning}.
    \item \textbf{``Lexicographer rule''} (patentees can define their own 
    terms---e.g., ``photocopy machine'').
    \item \textbf{Disclaimer/disavowal of specific meanings}.
\end{enumerate}

\paragraph{Role of Judge and Jury and the Standard of Appellate Review}

\begin{enumerate}
    \item Is claim interpretation a matter of law (for judges) or fact (for 
    juries)?\footnote{Casebook p. 296.}
    \item \emph{Markman v. Westview Instruments} (Fed. Cir. 1995): although 
    infringement claims must be tried by a jury, construction of patent claims 
    is best left to judges, since they have ``training in exegesis'' and are 
    likely to construct claims more uniformly.\footnote{Casebook pp. 296--97.}
    \item The Federal Circuit has held that it will review district court 
    findings of patent construction de novo (although it may be moving away from 
    the position that claim construction is purely a matter of 
    law).\footnote{Casebook p. 298.}
\end{enumerate}

\paragraph{Standards for Construing Claims; Sources of Construction: 
\emph{Phillips v. AWH Corporation}}
~\\\\
Courts can look to extrinsic sources, like dictionaries, to discern the 
meaning of claim terms. Patent construction is a matter of law, not fact 
(i.e., for judges, not juries).

\begin{enumerate}
    \item The dispute centered on the meaning of ``baffle'' in Phillips's 
    patent for ``security barriers''. The Federal Circuit initially found that 
    the use of the term in the patent meant that baffles could not be baffles 
    if they were attached at 90 degree angles (because one of their purposes 
    was to deflect projectiles, like bullets, and they can't deflect if 
    they're mounted at 90 degrees).\footnote{Casebook pp. 298--99.}
    \item In an en banc rehearing, the Federal Circuit here reversed.
    \item The key issue was whether the court should rely on the patent 
    specification to determine the meaning of the terms in the claim, or 
    whether it could look to extrinsic sources, like dictionaries or 
    treatises.\footnote{Casebook p.  300.}
    \item \emph{Texas Digital}: courts can seek definitions in extrinsic 
    sources, as long as the definitions are consistent with the usage in the 
    patent itself.\footnote{Casebook p. 301.}
    \item \emph{Markman} (holding that patent construction is a matter of law, 
    i.e., for judges, not juries, to decide) is reaffirmed.\footnote{Casebook p. 
    305.}
    \item ``Baffles'' doesn't just mean projectile-deflecting baffles; it can 
    also mean baffles mounted at 90 degrees.\footnote{Casebook p. 306.}
    \item Judge Mayer, dissenting: claim construction absolutely has a factual 
    component. The Federal Circuit has failed to develop a consistent standard. 
    By shifting its standard and reviewing each district court determination 
    novo, it wastes time and resources.\footnote{Casebook pp. 308--09.}
\end{enumerate}

\subsubsection{Literal Infringement: \emph{Larami Corp. v. Amron}}
~\\\\
There are two ways to infringe: (1) literal infringement and (2) the doctrine 
of equivalents.

\begin{enumerate}
    \item Amron sued Larami, claiming that Larami's SUPER SOAKERS infringed its 
    patents. According to Larami's motion for summary judgment, six of 35 claims 
    were in dispute, all regarding the hand pump mechanism.\footnote{Casebook 
    pp. 323--24.}
    \item There are two ways to establish infringement:
    \begin{enumerate}
        \item \textbf{Literal infringement},
        \item \textbf{The doctrine of equivalents}.
        \item The patent owner must ``show the presence of every element or its 
        substantial equivalent in the accused device.''\footnote{Casebook p. 
        324.} If a single element is missing, there is no infringement.
    \end{enumerate}
    \item Claim 1 describes a housing with a ``chamber therein for a 
    liquid~.~.~.'' Amron argued that Larami's design literally infringed Claim 
    1. The court held that Laramie's design did not infringe because it used an 
    external chamber.\footnote{Casebook pp. 324--25.}
\end{enumerate}

\subsubsection{The Doctrine of Equivalents}

\paragraph{Basic Issues: \emph{Graver Tank} and \emph{Warner-Jenkinson}}

\begin{enumerate}
    \item \emph{Graver Tank} (U.S. 1950): to avoid infringing, the copyist has 
    to make important and substantial changes. The rationale is to prevent new 
    inventors from defrauding patent holders by making trivial changes to 
    circumvent the patent's protections.\footnote{Casebook p. 328.}
    \begin{enumerate}
        \item \textbf{``Triple identity'' test}: the doctrine of equivalents 
        applies if a device ``performs substantially the same \emph{function} 
        in substantially the same \emph{way} to obtain the same 
        \emph{result}.''\footnote{Casebook p. 329.}
    \end{enumerate}
    \item In \emph{Warner-Jenkinson} (U.S. 1997), the Court articulated a new 
    test: ``Does the accused product or process contain elements 
    \textbf{identical or equivalent} to each claimed element of the patented 
    invention?'' The new test focuses on individual elements, so it's known as 
    the \textbf{``all elements rule.''}\footnote{Casebook pp. 329--30.}
\end{enumerate}

\paragraph{Prosecution History Estoppel: \emph{Festo Corp. v. Shoketsu}}

\begin{enumerate}
    \item How \textbf{prosecution history esoppel} works:\footnote{Casebook p. 
    333 and \emph{Understanding IP} 2F[2][C].}
    \begin{enumerate}
        \item During prosecution, applicants will sometimes amend their claims 
        to narrow their scope in order to avoid prior art.
        \item However, in later infringement suits, patent holders sometimes 
        try to expand the scope of their claims through the doctrine of 
        equivalents.
        \item Prosecution history estoppel prevents patent holders from 
        claiming subject matter that they surrendered during prosecution.
    \end{enumerate}
    \item \emph{Warner-Jenkinson}: prosecution history estoppel applies if the 
    patent holder limited claims through amendment during prosecution.
    \item \emph{Festo} (here): the Supreme Court held that prosecution history 
    estoppel is not an absolute bar to an infringement claim under the 
    doctrine of equivalents. Instead, the patent holder can rebut the 
    presumption of estoppel in three ways:\footnote{From \emph{Understanding 
    IP}.}
    \begin{enumerate}
        \item by showing that the equivalent was \textbf{unforeseeable} at the 
        application;
        \item that the rationale for the amendment bore only a 
        \textbf{tangential relationship} to the equivalent in question; or
        \item \textbf{some other reason} to be determined by future courts.
    \end{enumerate}
\end{enumerate}

\paragraph{After-Arising Technologies}

\begin{enumerate}
    \item Inventions that represent small incremental improvements over 
    existing patents are entitled to a narrower range of equivalents.
    \item Likewise, pioneering inventions are entitled to a broad range of 
    equivalents---i.e., courts will stretch to find infringement of pioneering 
    inventions.\footnote{Casebook p. 350--51.}
\end{enumerate}

\subsubsection{The ``Reverse'' Doctrine of Equivalents}

\begin{enumerate}
    \item Courts will sometimes avoid finding infringement even when the 
    second invention is within the literal terms of the 
    patent.\footnote{Casebook p. 355--58.}
\end{enumerate}

\subsection{Defenses}

\subsubsection{35 U.S.C. \S\ 282}

\begin{enumerate}
    \item (a) Presumption of validity.
    \item (b) Defenses:
    \begin{enumerate}
        \item (1) Noninfringement.
        \item (2) Invalidity.
        \item (3) Invalidity for failure to comply with \S\ 112 (written 
        description and enablement).
    \end{enumerate}
    \item Antitrust issues: patents confer market power. Market power can be 
    abused.
\end{enumerate}

\subsubsection{Inequitable Conduct: \emph{Therasense, Inc. v. Becton-Dickinson, 
Inc.}}

To prove inequitable conduct, an accused infringer must show (1) materiality 
(that the PTO would have thought the omitted fact was important) and (2) 
intent to deceive, by a clear and convincing evidence standard.

Inequitable conduct on one claim will render the entire patent unenforceable.

\begin{enumerate}
    \item Based in common law. Very powerful---a finding of inequitable 
    conduct renders a patent unenforceable.
    \item Causes: manufacture and suppression of evidence; ``fraud on the 
    Patent Office''; conspiracy to monopolize a product market (antitrust).
    \item Materiality: if the PTO had been aware of the facts, the challenged 
    claims would not have been allowed.
    \item Here, Therasense made arguments before the European Patent Office 
    that conflicted with its USPTO application. It failed to disclose the 
    European argument, which the court found to be inequitable conduct. So, 
    the patent was unenforceable.
\end{enumerate}

\subsubsection{Exhaustion of Patent Rights} 

\begin{enumerate}
    \item Key distinction between the physical object and the IP rights 
    embodied in that object.
    \item The first unrestricted sale of a patented product exhausts the 
    patentee's control. It can be resold and repaired without violating the 
    patent owner's rights.\footnote{Casebook p. 382.}
    \item Repair is permissible, reconstruction is not---but the line is 
    blurry.\footnote{Casebook p. 383.}
    \item Exhaustion applies only to \emph{sale}. It doesn't apply to 
    licenses.
\end{enumerate}

\paragraph{Exhaustion: \emph{Bowman v. Monsanto}}

\begin{enumerate}
    \item Monsanto customers were not allowed to replant or resell Roundup 
    Ready soybeans.\footnote{Supp. 12.}
    \item Bowman tried to circumvent the license by buying grain from a local 
    source, hoping that some of the seeds would be Roundup Ready.
    \item Bowman argued that as a downstream buyer, he was protected by patent 
    exhaustion/first sale.
    \item Held: exhaustion does not prevent the sale of patented items, but it 
    does prevent making copies, which is what Bowman did. The exhaustion 
    doctrine is limited to ``the particular item sold.''
\end{enumerate}

\subsection{Remedies}

\subsubsection{35 U.S.C. \S\ 283: Injunction}

\begin{enumerate}
    \item Courts can grant injunctions ``in accordance with the principles of 
    equity.'' See \emph{eBay} below.
\end{enumerate}

\subsubsection{35 U.S.C. \S\ 285: Attorney Fees}

\begin{enumerate}
    \item In ``exceptional cases,'' courts have discretion to award reasonable 
    fees to the prevailing party.
\end{enumerate}

\subsubsection{35 U.S.C. \S\ 286: Time Limitation on Damages}

\begin{enumerate}
    \item No recovery if the plaintiff files the complaint more than 
    \textbf{six years} after the alleged infringement.
\end{enumerate}

\subsubsection{35 U.S.C. \S\ 287: Limitations, Marking, Notice}

\begin{enumerate}
    \item (a) Notice and marking requirements, including new virtual marking 
    provisions.
\end{enumerate}

\subsubsection{Injunctions: \emph{eBay, Inc. v. MercExchange, LLC}}

Plaintiffs must satisfy a four-part test to win a permanent injunction.

The payoff is that courts no longer issue automatic injunctions. Courts still 
issue them in about 75\% of cases\footnote{See Merges PowerPoint.}, but they 
can prevent patentees from using minor patents to gain undue leverage.

\begin{enumerate}
    \item MercExchange held a patent involving the sale of goods through a 
    central authority (``consignment nodes''). It sued eBay for infringement.
    \item District court: the patent was valid and eBay (and Half.com) 
    infringed. It awarded damages but denied an injunction.
    \item Federal Circuit applied the \textbf{automatic injunction rule}, 
    which awards a permanent injunction upon an infringement finding.
    \item The Supreme Court rejected the automatic injunction rule and instead 
    implemented a four-part test. To win an injunction, the plaintiff must 
    show:
    \begin{enumerate}
        \item \textbf{Irreparable injury}.
        \item Remedies at law (i.e., monetary damages) are \textbf{inadequate}.
        \item Considering the \textbf{balance of hardships} between the 
        plaintiff and defendant, an injunction is warranted.
        \item A permanent injunction would \textbf{not disserve the public 
        interest}.
    \end{enumerate}
    \item Justice Kennedy, dissenting:
    \begin{enumerate}
        \item There are now cases where patentees use patents primarily to 
        obtain licensing fees. They might use an injunction as a tool to 
        charge ``exorbitant licensing fees.''\footnote{Casebook p. 405.}
        \item ``When the patented invention is \textbf{but a small component} 
        of the product the companies seek to produce and the threat of an 
        injunction is employed simply for \textbf{undue leverage} in 
        negotiations, legal damages may well be sufficient to compensate for 
        the infringement and an injunction may not serve the public 
        interest.''\footnote{Casebook p. 405.}
        \item The ``hold-up problem.''
    \end{enumerate}
\end{enumerate}

\subsubsection{Damages}

\paragraph{35 U.S.C. \S\ 284: Damages---Lost Profits and Reasonable Royalties}

\begin{enumerate}
    \item ``[T]he court shall award [the patentee] damages adequate to 
    compensate for the infringement but in no event less than a reasonable 
    royalty for the use made of the invention by the infringer~.~.~.~.''
    \item Two measures of damages:
    \begin{enumerate}
        \item Actual damages, i.e., lost profits.
        \item Reasonable royalty.
    \end{enumerate}
    \item Goal: find ``the difference between [patentee's] pecuniary condition 
    after the infringement, and what his condition would have been if the 
    infringement had not occurred.'' \emph{Yale Lock}.
    \item Award patentee's loss, not infringer's gain.
    \item \emph{Panduit}: the patentee wants to show that would have had sales 
    that the infringer made. To do so, the patentee must show the ``absence of 
    acceptable noninfringing substitutes.''
    \item Reasonable royalty is a fallback when the patentee can't show lost 
    profits---the ``hypothetical bargain'' principle.
\end{enumerate}

\paragraph{Willful Infringement: \emph{In re Seagate Technology, LLC}}
~\\\\
Willful infringement requires more than a showing of negligence.

\begin{enumerate}
    \item In cases of willful infringement, courts can increase damages up to 
    3x. 35 U.S.C. \S\ 286.
    \item Traditional rule: when a potential infringer has actual notice of 
    another's patent rights, he has an affirmative duty to exercise care to 
    determine whether he is infringing.
    \item This has led to punitive damages for a negligent failure to proceed 
    with due care.
    \item Here: this conception of negligence is at odds ``with the general 
    understanding of negligence in the civil context.''
    \item ``Accordingly, we overrule the standard set out in \emph{Underwater 
    Devices} and hold that proof of willful infringement permitting enhanced 
    damages requires at least a showing of objective recklessness. Because we 
    abandon the affirmative duty of due care, we also reemphasize that there 
    is no affirmative obligation to obtain opinion of 
    counsel.''\footnote{Casebook p. 418.} 
\end{enumerate}
