\section{Very Short Overview}

\subsection{Patent}

\begin{enumerate}
    \item \textbf{Elements of patentability}: subject matter, utility, written 
    description/enablement, novelty, nonobviousness.
    \item \textbf{Infringement}: claim interpretation, literal infringement, 
    doctrine of equivalents, prosecution history estoppel.
    \item \textbf{Defenses}: inequitable conduct, exhaustion.
    \item \textbf{Remedies}: injunctions, damages; willful infringement.
\end{enumerate}

\subsection{Copyright}

\begin{enumerate}
    \item \textbf{Requirements}: originality, fixation, formalities (notice, 
    publication, registration, deposit).
    \item \textbf{Subject matter}: idea/expression, merger doctrine, useful 
    article doctrine, government works; nine enumerated types.
    \item \textbf{Ownership and duration}: works for hire, joint works, 
    collective works; duration, division, transfer, renewal, termination of 
    transfer.
    \item \textbf{Rights of owners}: reproduction, derivative works, 
    distribution, public performance, display.
    \item \textbf{Indirect liabiity}: indirect, vicarious; substantial 
    noninfringing uses.
    \item \textbf{Fair use}: purpose and character, nature of work, amount, 
    effect on market; parodies, remixes, reverse engineering.
    \item \textbf{Digital copyright law}: anticircumvention (access control, 
    copy control), safe harbors, fair use, webcasting/compulsory licenses.
    \item \textbf{International copyright law}: Berne, TRIPS.
    \item \textbf{Damages}: injunctions (four \emph{eBay} factors), damages 
    (restitution and statutory), attorney fees.
\end{enumerate}

\subsection{Trademark}

\begin{enumerate}
    \item \textbf{Subject matter}: trademark, service mark, trade name, 
    slogan, certification mark, collective mark, trade dress, product 
    configuration, color/fragrance/sound.
    \item \textbf{Establishment of rights}: distinctiveness (distinctive, 
    non-distinctive, generic, cancellation, functionality), priority, USPTO 
    procedures, incontestability.
    \item \textbf{Infringement}: use in commerce, likelihood of confusion, 
    dilution (blurring, tarnishment, parodies), cybersquatting (ACPA, UDRP).
    \item \textbf{Defenses}: abandonment, lack of supervision, nominative use, 
    noncommercial use exception.
    \item \textbf{Remedies}: injunctions, damages, corrective advertising.
\end{enumerate}

\subsection{Trade Secret}

\begin{enumerate}
    \item \textbf{Structure of a claim}: subject matter (value, secrecy), 
    reasonable precautions, misappropriation.
    \item \textbf{Subject matter}: value, reasonable precautions; multiple 
    avenues of disclosure.
    \item \textbf{Misappropriation}: reasonable precautions, confidential 
    relationships, reverse engineering, IP assignment clauses, trailer 
    clauses, noncompete agreements, inevitable disclousre.
    \item \textbf{Agreements to keep secrets}: validity is contested when the 
    secret is no longer a secret.
    \item \textbf{Remedies}: injunctions, damages, attorney's fees; criminal 
    pentalties; head-start injunctions.
\end{enumerate}

\subsection{State Law and Federal Preemption}

\begin{enumerate}
    \item \textbf{Misappropriation}: quasi-property.
    \item \textbf{Protection by contract}: shrinkwrap agreements, statement of 
    agreement.
    \item \textbf{Idea submissions}: novelty (to the buyer vs. to the public), 
    contract before disclosure.
    \item \textbf{Right of publicity}: privacy vs. property, imitation, 
    transformative use test.
    \item \textbf{Copyright preemption}: Supremacy Clause, \S\ 301, two-part 
    test (subject matter and equivalence), limited enforcement.
    \item \textbf{Patent preemption}: no preemption of trade secrets, boat 
    hulls.
\end{enumerate}
